NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-30 aaV_main.tex
preprint number, mention exp analysis for the cuts

\preprint{
  \small
  \begin{flushright}
    ZU--TH--??\\ CERN-TH-2017-226
  \end{flushright}
}

\abstract{
Processes with three external electroweak gauge boson allow for a measurement of triple and quartic gauge
couplings. They can be used to constrain anomalous gauge couplings, where new physics might predominantly
couple to electroweak gauge bosons. In this paper we chose a class of such processes where we consider two photons
and an additional vector boson in the final state. As additional vector boson we consider either a third photon or a
$W$ or $Z$ boson. For the latter two cases we assume a leptonic decay of the boson. We calculate the next-to-leading
order QCD and electroweak corrections to these processes with a particular emphasize on the until now unknown 
electroweak corrections. We find that the electroweak corrections to the total cross section are moderate in the range of a few 
per cent at most, but can reach several tens of per cent in regions of phase space  that are particularly interesting
 in the context of new physics searches. In addition we investigate the difference between additive and multiplicative scheme 
 when combining
QCD and electroweak corrections and we asess the importance of photon induced contributions to these processes. 
}

>>>>

\preprint{
  \small
  \begin{flushright}
    ZU--TH 31/17\\ CERN-TH-2017-226
  \end{flushright}
}

\abstract{
Processes with three external electroweak gauge boson allow for a measurement of triple and quartic gauge
couplings. They can be used to constrain anomalous gauge couplings, where new physics might predominantly
couple to electroweak gauge bosons. In this paper we chose a class of such processes where we consider two photons
and an additional vector boson in the final state. As additional vector boson we consider either a third photon or a
$W$ or $Z$ boson. For the latter two cases we assume a leptonic decay of the boson. We calculate the next-to-leading
order QCD and electroweak corrections to these processes with a particular emphasis on the until now unknown 
electroweak corrections. We find that the electroweak corrections to the total cross section are moderate in the range of a few 
per cent at most, but can reach several tens of per cent in regions of phase space  that are particularly interesting
 in the context of new physics searches. In addition we investigate the difference between additive and multiplicative scheme 
 when combining
QCD and electroweak corrections and we assess the importance of photon induced contributions to these processes. 
}

### 2017-10-30 results.tex
preprint number, mention exp analysis for the cuts

Next we move on to diphoton production in association with 
a $W$ boson decaying leptonically.
In this context, we will representatively focus on $W^-$ bosons 
as we do not expect qualitatively different results for $W^+$ 
bosons. 
We define our fiducial phase space by the following. 
First, we require the presence of exactly one charged lepton, 
dressed with all photons in a cone of size $R=0.1$, with 
$\pT>20\,\text{GeV}$ and $|\eta|<2.5$. 
Among the remaining photons we require at least two identified 
ones, using the procedure described in Sec.\ \ref{sec:results:aaa}, 
only changing the transverse momentum requirements to 
$\pT>20\,\text{GeV}$ for both the leading and the subleading 
identified photon. 
We further demand the angular separation of both photons 
to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
the lepton to be $\Delta R(\ell,\gamma)>0.7$.
Furthermore we require the transverse mass of the lepton-neutrino system
to be larger than $40\, \text{GeV}$.
The inclusive cross sections and correction factors were 
detailed in Tab.\ \ref{tab:xsec}.

@@

Finally, we consider diphoton production in association with 
a $Z$ boson in its leptonic decay channel. 
In practise we look at lepton pair production including 
all non-resonant diagrams.
The fiducial phase space of our analysis is defined as follows. 
First, we require the presence of exactly one lepton pair 
of opposite charge, dressed with all photons in a cone of 
size $R=0.1$, with $\pT>20\,\text{GeV}$ and $|\eta|<2.47$. 
Their invariant mass must be larger than 40\,GeV. 
As in the case of \aaw production, we then require at least 
two identified photons among the remaining ones after dressing, 
using the procedure described in Sec.\ \ref{sec:results:aaa}, 
loosening the transverse momentum requirements to 
$\pT>15\,\text{GeV}$ for both the leading and the subleading 
identified photon. 
We further demand the angular separation of both photons 
to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
the lepton to be $\Delta R(\ell,\gamma)>0.4$.
The inclusive cross sections and correction factors were 
detailed in Tab.\ \ref{tab:xsec}.

>>>>

Next we move on to diphoton production in association with 
a $W$ boson decaying leptonically.
In this context, we will representatively focus on $W^-$ bosons 
as we do not expect qualitatively different results for $W^+$ 
bosons. 
We define our fiducial phase space by following experimental setups \cite{Aad:2015uqa}. 
First, we require the presence of exactly one charged lepton, 
dressed with all photons in a cone of size $R=0.1$, with 
$\pT>20\,\text{GeV}$ and $|\eta|<2.5$. 
Among the remaining photons we require at least two identified 
ones, using the procedure described in Sec.\ \ref{sec:results:aaa}, 
only changing the transverse momentum requirements to 
$\pT>20\,\text{GeV}$ for both the leading and the subleading 
identified photon. 
We further demand the angular separation of both photons 
to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
the lepton to be $\Delta R(\ell,\gamma)>0.7$.
Furthermore we require the transverse mass of the lepton-neutrino system
to be larger than $40\, \text{GeV}$.
The inclusive cross sections and correction factors were 
detailed in Tab.\ \ref{tab:xsec}.

@@

Finally, we consider diphoton production in association with 
a $Z$ boson in its leptonic decay channel. 
In practise we look at lepton pair production including 
all non-resonant diagrams.
The fiducial phase space of our analysis is defined as follows, again according 
to existing measurements \cite{Aad:2016sau}. 
First, we require the presence of exactly one lepton pair 
of opposite charge, dressed with all photons in a cone of 
size $R=0.1$, with $\pT>20\,\text{GeV}$ and $|\eta|<2.47$. 
Their invariant mass must be larger than 40\,GeV. 
As in the case of \aaw production, we then require at least 
two identified photons among the remaining ones after dressing, 
using the procedure described in Sec.\ \ref{sec:results:aaa}, 
loosening the transverse momentum requirements to 
$\pT>15\,\text{GeV}$ for both the leading and the subleading 
identified photon. 
We further demand the angular separation of both photons 
to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
the lepton to be $\Delta R(\ell,\gamma)>0.4$.
The inclusive cross sections and correction factors were 
detailed in Tab.\ \ref{tab:xsec}.
